\documentclass[10pt]{article}
\input{config}


\begin{document}


\begin{center}
\noindent {\huge\bfseries Shehbaz Tariq}
\vspace{2mm}\\
%Quantum Information Science\\
Postdoctoral Researcher at SnT\footnote{Interdisciplinary Centre for Security, Reliability and Trust (SnT)}\\
Kyung Hee University, South Korea\\
\end{center}

\noindent\parbox[t]{7cm}{%
  \small

Interdisciplinary Centre for \\ Security, Reliability and Trust \\
29, boulevard JF Kennedy \\ L-1855 LUXEMBOURG}
\hfill
\noindent\parbox[t]{6cm}{%
  \small
  \phantom{XXXXXXXa} Phone: +352 691 573600\\
\phantom{XXXXXXXa} Email: shehbaz.tariq@uni.lu \\ 
  \phantom{XXXXXXXXXXXXa} \href{https://github.com/ShehbazTariq}{\scalebox{1.5}{\faGithub}} \quad
  \href{https://scholar.google.com/citations?user=pOJIAhYAAAAJ&hl=en&oi=ao}{\scalebox{1.5}{\faGraduationCap}} \quad
  \href{https://www.linkedin.com/in/shehbaz-tariq/}{\scalebox{1.5}{\faLinkedin}}
}
\rule[-0.125in]{6.5in}{1pt}

%\vspace*{3mm}
\section*{Education}
\begin{mylist}


\item
    \edu{ Mar.~2021 -- Aug.~2025 }
    {Kyung Hee University, Yongin-si, Korea%\, \textnormal{[QS Rank: 270]}
    }
    {Ph.D. in Electronic and Information Convergence Engineering \,\,\,\quad\qquad\qquad\qquad CGPA: 4.28 / 4.50\\ Specialization in Quantum Computing and Machine Learning (MS leading to Ph.D)}
    {\vspace*{-5mm}
    %\begin{tabbing}
        %Title:\qquad \= Dequantumization of Discrete Weyl Quantum Channels\\
    %                %\>  Wireless Channels\\
    %    Advisor:   \> Professor Hyundong Shin
    %\end{tabbing}
    }


\item
    \edu{Aug.~2016 -- Sep.~2020}
    {University of Engineering and Technology, Peshawar, Pakistan,%\, \textnormal{[QS Rank: 334]}
    }
    {Bachelor of Engineering in Electrical Engineering
    \,\,\,\,\,\,\quad\qquad\qquad\qquad\quad\qquad\qquad CGPA: 3.87 / 4.00\\
    Final Year Project: AIOT-based monitoring app for smart cities}

\end{mylist}

\section*{Research Interests}

\noindent General research interest is quantum information processing for communication systems, emphasizing integrating quantum technologies with 6G and future networks, quantum network design and applications, and utilizing large AI models to develop integrated hybrid algorithms for next-generation networks.

\section*{Teaching Interests}
\noindent 
Quantum Computing,
Quantum Communications,
Large AI applications for Quantum  Information Processing,
Machine Learning Programming, 
and
Linear Algebra.


%\newpage 

\section*{Experience}

\subsection*{Work Experience}

\begin{mylist}

\item
\edu{Apr.~2025 -- Present}
{SnT,  University of Luxembourg, Kirchberg, Luxembourg}
{\emph{Postdoctoral Researcher} at 
    Signal Processing and Communications (SIGCOM) Research Group
}
{\vspace*{-5mm}
\begin{tabbing}
    Conduct research on Quantum MIMO systems and Quantum Reservoir Computing.\\
    Develop optimization and quantum machine learning techniques for wireless communication systems.\\
    Collaborate with academic and industrial partners on large-scale European research projects.
\end{tabbing}
}


\item
\edu{Mar.~2021 -- Mar.~2024}
{Kyung Hee University, Yongin-si, Korea}
{\emph{CQILAB Fellow \&  Research Assistant}\\
	Department of Electronics and Information Convergence Engineering%\\
	%	Communications and Coding Theory Laboratory
}
{\vspace*{-5mm}
	\begin{tabbing}
		Mentored undergraduate and graduate students in their research in quantum information sciences.\\
		Lead the group seminars on Quantum Machine Learning and AI. \\
  Managed and coordinated different teams working on large-scale R\&D projects including national\\ research foundation (NRF)-funded projects.
	\end{tabbing}}

\item
 \edu{Oct.~2023}
{Queen's University Belfast, Northern Ireland, UK}
{\emph{Visiting Scholar}\\
	 School of Electronics, Electrical Engineering and Computer Science%\\
	%	Communications and Coding Theory Laboratory
}
{\vspace*{-5mm}
	\begin{tabbing}
	   Organize seminars on Large AI applications for quantum computing, 6G and beyond. \\
  Managed and coordinated different teams working on quantum optimization for 6G applications.
	\end{tabbing}}



 












% \item
%     \edu{Aug.~2019 -- Sep.~2019}
%     {Pakistan Council of Scientific and Industrial Research (PCSIR), Peshawar}
%     {\emph{Technical Intern}\\
%     	Electrical Measurement \& Test Laboratory}
%     {\vspace*{-5mm}
%     \begin{tabbing}
%         Worked on the depth-image based 3D rendering and reduced-reference image quality assessment. 
%     \end{tabbing}}


    \item
    \edu{Mar.~2019 -- Aug.~2019}
    {University of Engineering and Technology, Peshawar, Pakistan}
    {\emph{Research Intern}\\
    	National Center of Artificial Intelligence (NCAI)}
    {\vspace*{-5mm}
    \begin{tabbing}
        Learned the core concepts of Machine Learning and AI. \\
        Assisted the Smart Flood and Safe City Teams. 
    \end{tabbing}}

\end{mylist}

% \subsection*{Research Projects}



% \subsubsection*{Ongoing Projects}
% \begin{enumerate}[ 1. ]


% 	\item \textbf{Wi-Qi BRL: Towards Integrating 6G Wireless and 2G Quantum} \\
% 	\textbf{Role:} Contributor in proposal, execution, and reporting\\
% 	\textbf{Short description:}  Funded by the National Research Foundation (NRF) of Korea, this project aims to seamlessly integrate 6G wireless networks with second-generation quantum technologies. This fusion seeks to revolutionize data transmission by enhancing speed, security, and computational capabilities.\\
% 	\textbf{Duration:} June 2022---February 2025.


%  	\item \textbf{ITRC: 6H Next Generation Mobile Communications Technology} \\
% 	\textbf{Role:} Contributor in execution, and reporting\\
% 	\textbf{Short description:}  Funded by  Institute for Information \& Communication Technology Planning \& evaluation (IITP) Korea, this project aims to foster a hyper-collaborative 6G society surpassing 5G, the center integrates and develops six "hyper" technologies—Hyper-Bandwidth, Hyper-Performance, Hyper-Connection, Hyper-Precision, Hyper-Trust, and Hyper-Intelligence—by uniting diverse technologies and AI across communication layers.\\
% 	\textbf{Duration:} July 2021---December 2028.


%  \item \textbf{BK21 FOUR: Convergence Engineering Institute for Emerging Communication Technology} \\
% 	\textbf{Role:} Contributor in execution, and reporting\\
% 	\textbf{Short description:}  Funded by the NRF Korea, this project aims to advance research and cultivate experts in convergence engineering and emerging communication technologies under the BK21 FOUR program.\\
% 	\textbf{Duration:} September 2020---August 2027.
% 	%
% 	%
% \end{enumerate}

% \subsubsection*{Past Projects}

% \begin{enumerate}
% 	\item \textbf{Foundations for Quantum Networking with Quantum Enigmata}\\
% 	\textbf{Role:} Contributor in execution, and reporting\\
% 	\textbf{Short description:} Funded by the NRF Korea, this project aimed to leverage different quantum paradoxes to develop foundations for quantum communications networks.\\
% 	\textbf{Duration:} March 2021---February 2024.
	
	
% \end{enumerate}







%\newpage
\section*{Publications \& Presentations}












%\subsection*{Selected Journal Papers (Published)}
\subsection*{Under Review/Preprints}	
\begin{enumerate}[ {[}1{]} ]
\item S.~Tariq, M.~Talha, S.~Chatzinotas, and H.~Shin, “Towards Quantum Enhanced Adversarial Robustness with Rydberg Reservoir Learning'' under review, 2026.  
\item S.~Tariq, J.~ur Rehman, and S.~Chatzinotas, “Quantum MIMO Diversity over Discrete-Variable Crosstalk Channels'', under review, 2026. 

\item J.~Kaldari, S.~Tariq, S.~Al-Kuwari, S.~Y.-C.~Chen, S.~Chatzinotas, and H.~Shin, “Quantum Reinforcement Learning: Recent Advances and Future Directions'' under review, 2026.

\item L.~Oleynik, S.~Tariq, and S.~Chatzinotas, “Optimal GHZ-State Distribution in LOSR Quantum Networks via Local Decoding from Information Sets'' under review, 2026.

\end{enumerate}

\subsection*{Journal Papers}	
\begin{enumerate}[ {[}1{]} ]

 \item S.~Tariq and S.~Chatzinotas, “Design and Optimization of Adaptive Diversity Schemes in Quantum MIMO Channels'' \emph{npj Quantum Information}, Jun. 2026.

\item N.~Lae, S.~Tariq, S.~N.~Paing, J.~W.~Setiawan, T.~Q.~Duong, and H.~Shin, “Counterfactual Quantum Secret Sharing'' \emph{IEEE Transactions on Communications}, Jun. 2025.  

\item B.~E.~Arfeto, S.~Tariq, U.~Khalid, T.~Q.~Duong, and H.~Shin, “GenSC-6G: A Prototype Testbed for Integrated Generative AI, Quantum, and Semantic Communication'' accepted for publication in \emph{IEEE Communications Magazine}, May. 2025.  

\item S.~Tariq, B.~E.~Arfeto, U.~Khalid, S.~Kim, T.~Q.~Duong, and H.~Shin, “Deep Quantum-Transformer Networks for Multi-Modal Beam Prediction in ISAC Systems'' \emph{IEEE Internet of Things Journal}, 18:29387–29401, Sep. 2024.  

\item S.~Tariq, A.~Farooq, J.~ur Rehman, T.~Q.~Duong, and H.~Shin, “Efficient Quantum State Estimation with Low-rank Matrix Completion'', \emph{EPJ Quantum Technology}, 11:50, Aug. 2024.  

\item S.~Tariq, U.~Khalid, B.~E.~Arfeto, T.~Q.~Duong, and H.~Shin, “Integrating Sustainable Big AI: Quantum Anonymous Semantic Broadcast'', \emph{IEEE Wireless Communications}, 31:86–99, Jun. 2024.  

\item S.~N.~Paing, J.~W.~Setiawan, S.~Tariq, M.~T.~Rahim, K.~Lee, and H.~Shin, “Counterfactual Anonymous Quantum Teleportation in the Presence of Adversarial Attacks and Channel Noise'', \emph{Sensors}, 22:7587, Oct. 2022.  



		


\end{enumerate}


\subsection*{Refereed Conference Proceedings}

\begin{enumerate}[ {[}1{]} ]
\item S.~Tariq, J.~ur Rehman, and S.~Chatzinotas, “Quantum MIMO Diversity Framework Using Approximate Cloning and Probabilistic Purification'' in \emph{2026 International Conference on Quantum Communications, Networking, and Computing (QCNC)}, Apr. 2026.

\item
B.~E.~Arfeto, S.~Tariq, and H.~Shin, '`Edge Diffusion Model for Enhanced Resolution in Semantic Communication'' in \emph{Proc. Korea Information and Communications Society (KICS) Fall Conference}, Gyeongju, Korea, Nov. 2024.

\item
M.~Talha, S.~Tariq, and H.~Shin, '`Recent Advances in Quantum Reservoir Computing'' in \emph{Proc. Korea Information and Communications Society (KICS) Fall Conference}, Gyeongju, Korea, Nov. 2024.

\item
P.~M.~Min, B.~E.~Arfeto, S.~Tariq, and H.~Shin, '`Quantum-Augmented LSTM Networks for Stock Price Forecasting'' in \emph{Proc. Korea Information and Communications Society (KICS) Fall Conference}, Gyeongju, Korea, Nov. 2024.

\item
S.~Tariq, B.~E.~Arfeto, H.~Jung, and H.~Shin, ``Beam Prediction in mmWave V2I Communications
with Quantum Transformer Networks,'' in \emph{Proc. International Conference on Information and Communication Technology Convergence (ICTC)}, Jeju, Korea, Oct. 2024

\item

S.~Tariq, J.~U.~Roh, and H.~Shin, ``Quantum Reinforcement Learning
for Digital Twin Placement in 6G Networks'' in \emph{Proc. Joint Conference on Communications and Information (JCCI)}, Busan, Korea, Apr. 2024.


\item

S.~Tariq, M.~S.~Ulum, A.~W.~Shaffar, W.~Park, S.~Kim, and H.~Shin, ``Multi-Agent Quantum Reinforcement Learning
for Digital Twin Placement in 6G Multi-Tier
Systems'' in \emph{Proc. EAI International Conference on Industrial Networks and Intelligent Systems (EAI INISCOM)}, Danang, Vietnam, Feb. 2024.


\item

S.~Tariq, A.~U.~Haque, H.~Jung, and H.~Shin, ``Quantum Approximate Optimization for Optimal
EV Charging Schedules'' in \emph{Proc. Joint Conference on Communications and Information (JCCI)}, Yeosu, Korea, Apr. 2023.


\item
U.~I.~Paracha, S.~ Tariq, M.~Choi, and H.~ Shin, 
``Bit-Flip Error Mitigation Using Deep Learning,''
in
\emph{Proc. Korea Information and Communication Society (KICS) Winter Conference},
Pyeongchang, Korea, Feb. 2023.

\item
A.~U.~Haque, S.~ Tariq, H.~Jung, and H.~ Shin, 
``Prototyping a Quantum Clustering Algorithm for
NISQ Computing''
in
\emph{Proc. Korea Information and Communication Society (KICS) Winter Conference},
Pyeongchang, Korea, Feb. 2023.

\item
S.~Tariq, K.~Lee, and H.~Shin, '`Deep Learning Assisted Quantum State Tomography'' in \emph{Proc. Korea Information and Communications Society (KICS) Fall Conference}, Gyeongju, Korea, Nov. 2022.

\item
A.~W.~Shaffar, S.~Tariq, and H.~Shin, '`Quantum Convolutional Neural Networks
for Binary Classification'' in \emph{Proc. Korea Information and Communications Society (KICS) Fall Conference}, Gyeongju, Korea, Nov. 2022.

\item 
S.~Tariq, A.~Farooq, and
H.~Shin, ``Robust Quantum State Tomography with
Linear Regression'' in \emph{Proc. Korea Information and Communication Society (KICS) Summer Conference},
Jeju, Korea, Jun. 2022.

\item 
A.~W.~Shaffar, M.~A.~Ullah,S.~Tariq, and
H.~Shin, ``Experimental Benchmarking Between IBM
Quantum Computing Systems'' in \emph{Proc. Korea Information and Communication Society (KICS) Summer Conference},
Jeju, Korea, Jun. 2022.


\item
 S.~ Tariq, A.~Farooq, J.~U.~Rehman, and H.~ Shin, 
``Error Analysis of Gate and Pulse
Model Quantum Circuits''
in
\emph{Proc. Korea Information and Communication Society (KICS) Winter Conference},
Pyeongchang, Korea, Feb. 2022.



\end{enumerate}

% \subsection*{Patents}

% \begin{enumerate}[ {[}1{]} ]
% \item
% H. Shin, J. ur Rehman, and F. Zaman, ``Method of quantum duplex
% coding and quantum communication system thereof'', Korea Patent 10-2260603, May
% 31, 2021.


% \item
% H.~Shin, J.~ur~Rehman, A.~Khan, and A.~Farooq, ``Method of Distributing Quantum Entanglement and Quantum Communication System Thereof,'' Korea Patent 10-2237183, Apr.~01, 2021.

% \item
% H.~Shin, J.~ur~Rehman, and M.~A.~Ullah, ``Quantum Synchronization Method Without Shared Phase Reference and Quantum Communication System Thereof,'' Korea Patent 10-2231135, Mar.~17, 2021.

% \item 
% H.~Shin, Y.~Jeong, and J.~ur~Rehman ``Quantum Channel Capacity Estimation Method and Quantum Communication System Thereof,'' Korea Patent 10-2231130, Mar.~17, 2021.

% \item
% H.~Shin, J.~ur~Rehman, and U.~Khalid, ``Quantum Measurement Method Using Perturbation Sensitivity and Quantum System Using Thereof,'' Korea Patent 10-2211060, Jan.~27, 2021.

% \item
% H.~Shin, J.~ur~Rehman, and A.~Khan, ``Method of Finding Entanglement Constraint in Multiqubit System and Quantum Communication System Thereof,'' Korea Patent 10-2203527, Jan.~11, 2021.


% \item
% H.~Shin, J.~ur~Rehman, and A.~Farooq, ``Method of distributing quantum entanglement and quantum communication system,'' Korea Patent 10-2158777, Sep.~16, 2020.


% \item
% H.~Shin, Y.~Jeong, J.~Kim, A.~Farooq, and J.~ur~Rehman, ``Method of distributing optimally quantum entanglement and quantum communication system,'' Korea Patent 10-2122799, Jun.~09, 2020.



% \item 
% H.~Shin, Y.~Jeong, and J.~ur~Rehman, `` Method of securing quantum information and system thereof,'' Korea Patent 10-2017835, Aug.~28, 2019.



% \item
% H.~Shin, S.~Qaisar, Y.~Jeong, and J.~ur~Rehman, ``Method and device for deterministic secure quantum communication,'' Korea Patent 10-1965229, Mar.~25, 2019.


% \item
% H.~Shin, J. ur Rehman, S. Qaisar, and Y.~Jeong, ``Method and device of performing quantum key distribution (QKD) among plurality of devices,''  Korea Patent 10-1924100, Nov.~26, 2018.


% \item
% H.~Shin, J.~ur Rehman, S.~Qaisar, and Y.~Jeong, ``Method of distributing key for multi-party in quantum communication, method of performing quantum communication using the same and quantum communication system performing the same,'' Korea Patent 10-1836947, Mar.~5, 2018.

% \item
% H.~Shin, S.~Qaisar, J.~ur Rehman, and Y.~Jeong, ``Method of distributing key with low-power in quantum communication, method of performing quantum communication using the same and quantum communication for performing the same,'' Korea Patent 10-1826065, Jan.~31, 2018.

% \item
% H.~Shin, J.~ur Rehman, and Y.~Jeong, ``Method of distributing key in quantum communication, method of preforming quantum communication using the same and quantum communication system performing the same,'' Korea Patent 10-1808544, Dec.~7, 2017.



% \end{enumerate}

\subsection*{Theses}

\begin{enumerate}

\item

S.~Tariq, `Hybrid Quantum-Classical Computing
for 6G Networks: Algorithms,
Applications, and System Integration,'' Ph.D. dissertation, Department of Electronics and Information Convergence Engineering, Kyung Hee University, Yongin-si, Korea, Feb. 2025, Thesis
  Advisor: Professor Hyundong Shin.

\item

S.~Tariq, ``AIOT-based monitoring app for smart cities,'' Bachelor's thesis, Department of Electrical Engineering, University of Engineering and Technology, Peshawar, Pakistan, Aug. 2020, Thesis
  Advisor:  Dr. Muhammad Amir.

\end{enumerate}


%\section*{Professional \& Scholarly Activities}









% \subsection*{Professional Reviews}

% \begin{mylist}
	
% 	\item
	
% 	Reviewer of \textsc{IEEE Journal on Selected Areas in
% 		Communications}, \textsc{IEEE Access}, \textsc{IEEE Journal of Selected Topics in Signal Processing}.
	
	

% \end{mylist}

\section*{Certifications}
\begin{mylist}
\item \shref{Qiskit Global Summer School (2024)  | IBM}{https://www.credly.com/badges/5d50d024-7294-4a57-910c-916520f431af}
\item \shref{Variational Algorithm Design (2024) | IBM}{https://www.credly.com/badges/50baa768-75e1-4fb0-8c99-e642472aae86}
\item \shref{AI Programming with Python (2023) | Udacity}{https://graduation.udacity.com/confirm/P2EETRSX}
\item \shref{Generative AI for Everyone (2023) | DeepLearning.AI}{https://www.coursera.org/account/accomplishments/certificate/NNZFHA5V2CNV}
\item \shref{XCS229 - Machine Learning (2022) | Stanford Online}{https://digitalcredential.stanford.edu/check/351B041A3F6264F10C404E292A61E056BBE74E737CB477480DB5B3282AA78278RGpuZGpadFhTN016NXRDWmRVRjkyYmNuZTVzTHFXeTExem1yZE5nUy9PaXR0Y0xT}


\end{mylist}


\section*{Honors and Awards}

\begin{mylist}

\item

Two-time Recipient of Khreative U+ Creative Innovation KHU-Fellowship (2022 \& 2023)

\item

Doctoral Research Scholarship, BrainKorea21 Plus, 2021 -- 2025

\item

Graduate Student Scholarship, Kyung Hee University, 2021 --
2025

\item 
National Grassroots ICT Research Initiative FYP Grant, 2020 

\item 
STOORI DA PAKHTUNKHWA Provisional Government Scholarship, 2016

\item 
STOORI DA MARDAN District Government Scholarship, 2016


%\item

%Undergraduate Merit Scholarship, National University of Sciences and Technology, Fall 2009

\end{mylist}



%\ifthenelse{\value{REF} = 1}{\newpage
\section*{Professional References}
\begin{enumerate}
	
    \item[1.] Prof. Symeon Chatzinotas\\[-0.8cm]
\begin{tabbing}
    \textbf{Designation:} \= Full Professor and SIGCOM Head\\
    \textbf{Affiliation:} \> Interdisciplinary Centre for Security, Reliability and Trust (SnT), \\
        \> University of Luxembourg, Luxembourg\\
    \textbf{Relation:} \> Supervisor\\
    \textbf{email:} \> symeon.chatzinotas@uni.lu\\
    \textbf{Phone:} \> (+352) 46 66 44 5767
\end{tabbing}

	
	\item[2.] Prof. Hyundong Shin\\[-0.8cm]
	\begin{tabbing}
		\textbf{Designation:} \= Full Professor and Dean\\
		\textbf{Affiliation:} \> Department of Electronics and Information Convergence Engineering, \\
            \>  Kyung Hee University, South Korea\\
		\textbf{Relation:} \> Ph.D. Advisor\\
		\textbf{email:} \> hshin@khu.ac.kr\\
		\textbf{Phone:} \> +82-31-201-3812
	\end{tabbing}

 	\item[3.] Prof. Trung Q. Duong \\[-0.8cm]
	\begin{tabbing}
		\textbf{Designation:} \= Full Professor\\
		\textbf{Affiliation:} \> Faculty of Engineering and Applied Science, \\
		\>  Memorial University of Newfoundland, Canada\\
		\textbf{Relation:} \> Research Collaborator\\
		\textbf{email:} \> tduong@mun.ca\\
		\textbf{Phone:} \> (+1) 709 864 2391
	\end{tabbing}
 

 	\item[4.] Dr. Junaid ur Rehman\\[-0.8cm]
	\begin{tabbing}
		\textbf{Designation:} \= Assistant Professor\\
		\textbf{Affiliation:} \> Department of Electrical Engineering, \\
		\> King Fahd University of Petroleum and Minerals,\\
              \>  Dhahran, Saudi Arabia\\
		\textbf{Relation:} \> Research Collaborator\\
		\textbf{email:} \> junaid.urrehman@kfupm.edu.sa\\
		\textbf{Phone:} \> (+966) 13 860 5360
	\end{tabbing}
	%
	%
	%

\end{enumerate}
%}{\section*{Professional References}
%Available upon request.}
\end{document}
